\documentclass[11pt,a4paper]{article}

\usepackage[left=0.70in,right=0.70in,top=0.50in,bottom=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{microtype}

\definecolor{linkblue}{HTML}{003A80}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\sloppy

\titleformat{\section}
  {\large\scshape\bfseries}
  {}{0em}{}[\vspace{-0.42em}\rule{\linewidth}{0.4pt}\vspace{-0.38em}]
\titlespacing*{\section}{0pt}{0.92em}{0.48em}

\setlist[itemize]{
  leftmargin=1.10em,
  itemsep=0.18em,
  topsep=0.14em,
  parsep=0em,
  partopsep=0em
}
\renewcommand\labelitemi{$\circ$}

\newcommand{\cvitem}[4]{%
  \item \begin{tabularx}{\linewidth}[t]{@{}>{\RaggedRight\arraybackslash}X@{\hspace{0.8em}}>{\RaggedLeft\arraybackslash}p{2.10in}@{}}
  \textbf{#1} & \textit{#2}\\
  \textit{#3} & #4
  \end{tabularx}\vspace{-0.18em}
}

\newcommand{\cvitemplain}[2]{%
  \item \begin{tabularx}{\linewidth}[t]{@{}>{\RaggedRight\arraybackslash}X@{\hspace{0.8em}}>{\RaggedLeft\arraybackslash}p{2.10in}@{}}
  \textbf{#1} & \textit{#2}
  \end{tabularx}\vspace{-0.18em}
}

\newcommand{\projectitem}[2]{%
  \item \begin{tabularx}{\linewidth}[t]{@{}>{\RaggedRight\arraybackslash}X@{\hspace{0.8em}}>{\RaggedLeft\arraybackslash}p{2.10in}@{}}
  \textbf{#1} & \textit{#2}
  \end{tabularx}\vspace{-0.14em}
}

\newcommand{\awarditem}[2]{%
  \item \begin{tabularx}{\linewidth}[t]{@{}>{\RaggedRight\arraybackslash}X@{\hspace{0.8em}}>{\RaggedLeft\arraybackslash}p{1.65in}@{}}
  #1 & #2
  \end{tabularx}\vspace{-0.14em}
}

\newcommand{\paperitem}[2]{%
  \noindent\makebox[2.2em][l]{\textbf{[#1]}}#2\par\vspace{0.34em}
}

\begin{document}

\begin{center}
    {\Huge \bfseries Doeun Kim}\\[0.38em]
    \href{mailto:dragonhope@naver.com}{dragonhope@naver.com} \; | \; Seoul, South Korea
\end{center}
\vspace{0.16em}

\section*{Education}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
  \cvitemplain{Sogang University}{Mar 2021 -- Present}
  \vspace{-0.08em}
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
  \textit{B.S. in Mathematics and Computer Science} & Seoul, South Korea
  \end{tabularx}
  \begin{itemize}
    \item \textbf{GPA:} 4.16 / 4.30; \textbf{Current:} 7th semester
    \item \textbf{Leave of Absence:} Mandatory military service, Oct 2022 -- Apr 2024
  \end{itemize}
\end{itemize}

\section*{Research Interests}
Causal Machine Learning, Causal Foundation Models, Graph Representation Learning, Natural Language Processing

\section*{Research Experience}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
  \cvitem{Causality Lab, SNU Graduate School of Data Science}{Jul 2025 -- Present}{Undergraduate Researcher (Advisor: Prof. Sanghack Lee)}{Seoul, South Korea}
  \begin{itemize}
    \item Investigated failure modes of Causal Foundation Models (CFMs) under post-treatment conditioning, query misspecification, and causal structure ambiguity.
    \item Studied graph-aware approaches for incorporating structural information into PFN-style causal foundation models.
    \item Co-authored ICML 2026 workshop work on CFM robustness and query specification.
  \end{itemize}

  \cvitem{SKI-ML Lab, SNU Graduate School of Data Science}{Jun 2024 -- Aug 2024}{Intern (Advisor: Prof. Jay-Yoon Lee)}{Seoul, South Korea}
\end{itemize}

\section*{Teaching \& Service Experience}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
  \cvitem{Sogang University}{Winter 2024, Summer 2025}{Teaching Assistant, Introduction to AI Programming (COR1010)}{Seoul, South Korea}
  \begin{itemize}
    \item Assisted course operation, programming assignment support, and student Q\&A for an introductory AI programming course.
  \end{itemize}

  \cvitem{KATUSA, Republic of Korea Army}{Oct 2022 -- Apr 2024}{Military Service, Korean Augmentation to the U.S. Army}{South Korea}
  \begin{itemize}
    \item Completed mandatory military service in a bilingual U.S.-ROK Army environment.
  \end{itemize}
\end{itemize}

\section*{Workshop Papers}
\paperitem{1}{\textbf{A Structural View of Query Misspecification in Causal Foundation Models.} \textit{ICML 2026 Workshop on Structured Probabilistic Inference \& Generative Modeling (SPIGM), 2026.}\\
\textbf{Causal Foundation Models Perform Better without Post-treatment Variables.} \textit{ICML 2026 Workshop on Foundation Models for Structured Data (FMSD), 2026.}}

\section*{Projects}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]

  \projectitem{Do-PFN Really Do Causality?}{Fall 2025}
  \begin{itemize}
    \item Collaborated with Causality Lab interns on a research project examining whether Do-PFN/PFN-style models exhibit causal reasoning behavior.
  \end{itemize}

  \projectitem{FA-AL-MOT: Multimodal Fashion Price Prediction}{Fall 2025}
  \begin{itemize}
    \item Built a multimodal AI model for C2C fashion resale price prediction and product attribute classification using image and text features.
    \item Used CLIP fusion, LLM-based attribute restoration, and GPU-accelerated deep learning; achieved $R^2 = 0.8904$ for price prediction.
  \end{itemize}

  \projectitem{DIGIRO: Real-Time Notification Service}{Summer 2025}
  \begin{itemize}
    \item Architected and developed a real-time notification service using FastAPI (Python) and PostgreSQL to aggregate and serve live data for Seoul's Jongno-gu district.
    \item Containerized the application's backend, crawler, and database services using Docker and managed deployment orchestration with Kubernetes for scalability and reliability.
    \item Integrated multiple external sources, including Seoul Public Data and Kakao Maps APIs, to provide users with an interactive map visualizing protest locations, routes, and traffic control areas.
  \end{itemize}

  \projectitem{News Summarization with GPT-2 \& Knowledge Distillation}{Spring 2025}
  \begin{itemize}
    \item Enhanced GPT-2 summarization on CNN/DailyMail dataset; sequence-level distillation from LLaMA3-8B improved ROUGE-1 by 20.6\% and METEOR by 54.6\%.
    \item Analyzed decoder-only model limitations and cross-model distillation challenges.
  \end{itemize}

  \projectitem{Convenience-Store Management Application}{Spring 2025}
  \begin{itemize}
    \item C/MySQL CLI tool for business analytics queries.
  \end{itemize}

  \projectitem{Automated Lighting Control via Object Detection}{Winter 2024}
  \begin{itemize}
    \item Integrated YOLO + ByteTrack with a line-crossing counter to trigger lights based on occupancy.
  \end{itemize}

  \projectitem{RAG Chatbot for Academic Catalog}{Fall 2024}
  \begin{itemize}
    \item Built a RAG pipeline with SOLAR embeddings, SOLAR API, ChromaDB, and Streamlit UI for real-time Q\&A on Academic Catalog.
  \end{itemize}

  \projectitem{Fine-Grained Classification}{Spring 2024}
  \begin{itemize}
    \item Developed ResNet-101 classifier on CUB-200-2011; augmented data with Gaussian noise to defend against PGD attacks.
  \end{itemize}
\end{itemize}

\section*{Scholarships}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
\awarditem{\textbf{KT Digital Talent Scholarship}, KT (Full Funding)}{Spring 2025 -- Present}
\end{itemize}

\section*{Awards \& Honors}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
\awarditem{\textbf{Outstanding Scholar}, KT Group Hope Sharing Foundation (selected as one of 4 outstanding scholars)}{Jan 2026}
\awarditem{\textbf{Excellence Award in Inquiry Community Program (for \textit{Automated Lighting Control via Object Detection})}, Sogang University}{Jan 2026}
\awarditem{\textbf{Dean's List}, College of Natural Sciences, Sogang University (Year of 2021)}{2022}
\end{itemize}



\section*{Skills}
\begin{itemize}[label=$\bullet$, leftmargin=0.70em]
  \item \textbf{Programming \& Tools:} C/C++, Python, MySQL, SAS, MATLAB
  \item \textbf{Languages:} Korean (Native), English (Fluent)
\end{itemize}

\end{document}
